### 2021-02-11 cover_letter.tex
Update release version.

  \item To demonstrate the utility and efficiency of {\it ensmallen} on real-world
problems, we added an experiment comparing {\it ensmallen} to other toolkits in the context of training 
a logistic regression model on real-world datasets from the UCI dataset
repository.  While we would like to add even more experiments,
we are constrained by the four page limit for this manuscript.
However, additional experiments for interested readers are given
in the accompanying technical report, which is cited at the end of the conclusion.

@@

  \item We have addressed the test failures reported by Reviewer 1.
Many tests in {\it ensmallen} are probabilistic, where a random initial point is used,
followed by checking that an optimizer is able to reach somewhere
close to the expected minimum.  However, given the nature of many optimizers,
convergence to an expected point is not always guaranteed.
To address this, we overhauled our test infrastructure such that we are now able
to run our tests 1000 times with unique random seeds and no failures.
The revamped test suite is part of the latest release, ensmallen 2.15.2.
(The changes can be viewed in \url{https://github.com/mlpack/ensmallen/pull/249}).

>>>>

  \item To demonstrate the utility and efficiency of {\it ensmallen} on real-world
problems, we added an experiment comparing {\it ensmallen} to other toolkits in the context of training 
a logistic regression model on real-world datasets from the UCI dataset
repository.  While we would like to add even more experiments,
we are constrained by the four page limit for this manuscript.
However, additional experiments for interested readers are given
in the accompanying technical report, which is cited in the conclusion.

@@

  \item We have addressed the test failures reported by Reviewer 1.
Many tests in {\it ensmallen} are probabilistic, where a random initial point is used,
followed by checking that an optimizer is able to reach somewhere
close to the expected minimum.  However, given the nature of many optimizers,
convergence to an expected point is not always guaranteed.
To address this, we overhauled our test infrastructure such that we are now able
to run our tests 1000 times with unique random seeds and no failures.
The revamped test suite is part of the latest release, ensmallen 2.16.0.
(The changes can be viewed in \url{https://github.com/mlpack/ensmallen/pull/249}).
